---
title: "PCA and Clustering"
output: html_document
editor_options: 
  chunk_output_type: console
---



```{r setup, include=FALSE}
# Knitr options
### Generic preamble
Sys.setenv(LANG = "en") # For english language
options(scipen = 5) # To deactivate annoying scientific number notation

# rm(list=ls()); graphics.off() # get rid of everything in the workspace
if (!require("knitr")) install.packages("knitr"); library(knitr) # For display of the markdown

### Knitr options
knitr::opts_chunk$set(warning=FALSE,
                     message=FALSE,
                     fig.align="center"
                     )
```

Loading in the packages 

```{r, include = FALSE}
library(tidyverse) 
library(magrittr) 
library(lubridate)
library(GGally)
library(FactoMineR)
library(factoextra)
library(dplyr)
library(uwot)
library(Hmisc)
library(skimr)
```

Loading in the data

```{r, message= FALSE, warning = FALSE, comment= FALSE}
data <- read_csv("Data/sti_scoreboard.csv", show_col_types = FALSE)
list <- read.csv("https://stiplab.github.io/datastories/STI.Scoreboard/Inventory.csv", header = TRUE, sep = ",")
country <- read_csv("https://raw.githubusercontent.com/lukes/ISO-3166-Countries-with-Regional-Codes/master/all/all.csv", show_col_types = FALSE) %>% select(name, `alpha-3`, region) %>% rename(COUNTRY = `alpha-3`, COUNTRY_FULL = "name")
doc_df <- read_csv("Data/doc_cat_2.csv", show_col_types = FALSE)
```

## Data preparation
```{r, include = FALSE}
INDICATOR_LIST <- c("COPAT_XPCT", "H_XFB", "B_XFG", "G_FBXGDP", "B_XGDP", "G_XGDP", "GV_XFB", "GV_XGDP")
```

selecting indicators and rearranging dataset
```{r}
data <- data %>% filter(INDICATOR %in% INDICATOR_LIST)


data <- data %>% unique() %>% pivot_wider(id_cols =c(COUNTRY, YEAR), names_from = INDICATOR, values_from = Value)


data <- data %>% filter(COUNTRY != "G20_OECD" & COUNTRY != "G20_NON_OECD" & COUNTRY != "G20" & COUNTRY != "G-7" & COUNTRY != "EU28" & COUNTRY != "EU27_2020" & COUNTRY != "EU27" & COUNTRY != "EU" & COUNTRY != "EA19" & COUNTRY != "E23" & COUNTRY != "E23" & COUNTRY != "E22" & COUNTRY != "E15"  & COUNTRY != "OECD")
```


impute missing values
```{r}
data <- data %>%
  fill(INDICATOR_LIST, .direction = "down") %>% 
  fill(INDICATOR_LIST, .direction = "up") 
```

Five year Time-frame ID's
```{r}
data <- data %>% filter(YEAR >=2001 & YEAR <=2020) %>%
  mutate(ID = ifelse(YEAR >= 2001 & YEAR <= 2005, 1, 
                                    ifelse(YEAR >= 2006 & YEAR <= 2010, 2, 
                                    ifelse(YEAR >= 2011 & YEAR <= 2015, 3, 
                                    ifelse(YEAR >= 2016 & YEAR <= 2020, 4,0)))))

data_all <- data %>% select(-YEAR) %>% group_by(COUNTRY, ID) %>% 
  summarise(across(.cols = everything(), ~ mean(.x, na.rm =TRUE)))
```


codebook for indicators selected
```{r, include = FALSE}
list <- list %>% select(SerieCode, IndicatorLabel)

codebook <- data_all %>% select(-ID) %>% pivot_longer(!COUNTRY, "INDICATOR") 

codebook <- codebook[,2]

codebook <- codebook %>% distinct()

codebook <- codebook %>% left_join(list, by = c("INDICATOR" = "SerieCode"))

codebook <- codebook %>% distinct()

```


Knowledge transfer triangulation
```{r}
kt <- doc_df %>% filter(assigned_category == "Knowledge Transfer")
kt <- kt %>% select(CountryCode, StartDateYear) %>% rename(COUNTRY = CountryCode, START = StartDateYear)
kt <- kt %>% group_by(COUNTRY, START) %>% summarise(n_kt =n())
kt <- kt %>% filter(START > 2000)
```

```{r}
data_kt <- data %>% left_join(kt, by = c("COUNTRY" = "COUNTRY", "YEAR" = "START")) 
#data_kt <- data_kt %>% select(COUNTRY, YEAR, n_kt, co_create_1, co_create_2, co_create_3, co_create_4, co_all)
data_kt %<>% mutate(n_kt = ifelse(is.na(n_kt), 0, n_kt))
data_kt %<>% mutate(n_kt_lag1 = Lag(n_kt, -1), 
                    n_kt_lag2 = Lag(n_kt, -2), 
                    n_kt_lag3 = Lag(n_kt, -3))
```


co-creation triangulation
```{r}
co_create <- doc_df %>% filter(assigned_category == "Co-creation")
co_create <- co_create %>% select(CountryCode, StartDateYear) %>% rename(COUNTRY = CountryCode, START = StartDateYear)
co_create <- co_create %>% group_by(COUNTRY, START) %>% summarise(n_cocreate =n())
co_create <- co_create %>% filter(START > 2000)
```

```{r}
data_co <- data %>% left_join(co_create, by = c("COUNTRY" = "COUNTRY", "YEAR" = "START")) 
data_co <- data_co %>% filter(YEAR > 2000)

#data_co <- data_co %>% select(COUNTRY, YEAR, n_cocreate)#, co_create_1, co_create_2, co_create_3, co_create_4, co_all)
data_co %<>% mutate(n_cocreate = ifelse(is.na(n_cocreate), 0, n_cocreate))
data_co %<>% mutate(n_cocreate_lag1 = Lag(n_cocreate, -1), 
                    n_cocreate_lag2 = Lag(n_cocreate, -2), 
                    n_cocreate_lag3 = Lag(n_cocreate, -3))
```


## PCA

Doing a PCA analysis with standardized scaling 
```{r}
res_pca <- data_all[,3:10] %>%
  select_if(is_numeric) %>%
  PCA(scale.unit = TRUE, ncp = 3, graph =FALSE)

## Scree-plot with 10 components

scree_plot <- res_pca %>% 
  fviz_screeplot(addlabels = TRUE,
                 ncp = 10,
                 ggtheme = theme_gray())
scree_plot
```


Adding the dimensions to the dataset

```{r}
coord_pca <- res_pca[["ind"]][["coord"]]
data_all$dim1 <- coord_pca[,1]
data_all$dim2 <- coord_pca[,2]
data_all$dim3 <- coord_pca[,3]
```

The percentage of variance explained and the cumulative percentage of variance explained can be seen in the table below

```{r}
res_pca$eig[1:7,3] %>% as_tibble() %>% round(1)

```


EIGENVALUES 
```{r, warning=FALSE, message=FALSE}
res_pca$eig[1:5, 1:2] %>% as_tibble() %>% rownames_to_column(var = "component") %>% select(component, eigenvalue)
```


```{r}
plot <- res_pca %>%
  fviz_pca_biplot(alpha.ind = "cos2",
                  col.ind = "contrib",
                  gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
                  geom = "point",
                  ggtheme = theme_bw())

plot
```
 
Coloring points by region
```{r}
country_coord <- data.frame(x = res_pca[["ind"]][["coord"]][,1], 
                            y = res_pca[["ind"]][["coord"]][,2], 
                            #country = data1$COUNTRY, 
                            #year = data1$YEAR)
                            country = data_all$COUNTRY)

country_coord %<>% left_join(country, by = c("country" = "COUNTRY"))
```

```{r}
country_coord %>% 
ggplot(aes(x = x, y = y, color = region)) + 
  geom_point(size = 5) + 
#theme(legend.position = "none")
  theme()
```
 

## Cluster Analysis
 

Doing a hierarchical clustering based on the first 3 principal components

```{r, include = FALSE}
res_hcpc <- res_pca %>% 
  HCPC(nb.clust = -1,
       graph = FALSE) 
```

Adding clusters to the observations
```{r}
data_all$cluster <- res_hcpc[["data.clust"]][["clust"]]
data_all %<>% left_join(country %>% select(COUNTRY, COUNTRY_FULL))
```

calculating convex hull
```{r}
hull_data <- 
  data_all %>%
  drop_na() %>%
  group_by(cluster) %>% 
  slice(chull(dim1, dim2))
```

graph on cluster-membership
```{r}
data_all %>%
  ggplot(aes(x = dim1, y = dim2, color = cluster)) + 
  geom_point() + 
  labs(x = "dim1 (28.7%)", y = "dim2 (26.3%)") + 
  geom_polygon(data = hull_data, aes(fill = cluster,
                   colour = cluster),
               alpha = 0.3,
               show.legend = FALSE) +

  theme_bw()
```

**Which countries belong to each of the clusters?**
```{r}
summary <- table(data_all$COUNTRY, res_hcpc[["data.clust"]][["clust"]])



summary_df <- data.frame(Clust_1 = summary[,1], 
                         Clust_2 = summary[,2],
                         Clust_3 = summary[,3])#, 
                         #Clust_4 = summary[,4])

summary_df <- summary_df %>% rownames_to_column("COUNTRY") 

summary_df <- summary_df %>% left_join(country, by = "COUNTRY") %>% select(COUNTRY, COUNTRY_FULL, region, Clust_1, Clust_2, Clust_3)#, Clust_4)
```

```{r}
summary_df %>% filter(Clust_3 >= 1) %>% select(COUNTRY_FULL, Clust_1, Clust_2, Clust_3) %>% arrange(desc(Clust_3))
```

```{r}
summary_df %>% filter(Clust_2 >= 1) %>% arrange(desc(Clust_2))
```

```{r}
summary_df %>% filter(Clust_3 >= 1)
```


### CLUSTER-level characteristics
```{r}
stat <- data_all %>% select(-COUNTRY, -ID) %>% group_by(cluster) %>% 
  summarise(across(.cols = everything(), ~mean(.x, na.rm = TRUE)))

stat <- cbind(stat, rowMeans(stat[,3:13])) %>% select(-COUNTRY)

stat <- stat %>% rename("RowMeans" = `rowMeans(stat[, 3:13])`)
```

```{r}
stat 
```

```{r}
stat_left <- stat[,1:5] 
stat_left <- stat_left %>% cbind(rowMeans(stat_left[,2:5]))
stat_left <- stat_left %>% rename("RowMeans" = `rowMeans(stat_left[, 2:5])`)
```

```{r}
stat_left
```

```{r}
stat_right <- stat[,c(1,6:9)]
stat_right <- stat_right %>% cbind(rowMeans(stat_right[,2:5]))
stat_right <- stat_right %>% rename("RowMeans" = `rowMeans(stat_right[, 2:5])`)
```

```{r}
stat_right
```

**Number of observations within each cluster**

```{r}
data_all %>% filter(cluster == 1) %>% nrow()
```

```{r}
data_all %>% filter(cluster == 2) %>% nrow()
```
```{r}
data_all %>% filter(cluster == 3) %>% nrow()
```


Adding Co-creation information from the STIP

```{r}
data_co_five <- data_co %>% filter(YEAR >=2001 & YEAR <=2020) %>%
  mutate(ID = ifelse(YEAR >= 2001 & YEAR <= 2005, 1, 
                                    ifelse(YEAR >= 2006 & YEAR <= 2010, 2, 
                                    ifelse(YEAR >= 2011 & YEAR <= 2015, 3, 
                                    ifelse(YEAR >= 2016 & YEAR <= 2020, 4,0)))))

data_co_five %<>% select(COUNTRY, ID, n_cocreate) %>% group_by(COUNTRY, ID) %>% 
  summarise(across(.cols = everything(), ~ mean(.x, na.rm =TRUE)))

data_all %<>% left_join(data_co_five, by = c("COUNTRY" = "COUNTRY", "ID" = "ID"))

data_all %>% group_by(cluster) %>% summarise(n = n(), avg = sum(n_cocreate) / n)
```

correlation between dimensions and cocreation
```{r}
reg <- lm(n_cocreate ~ dim1, data_all)
summary(reg)
```


ADDING knowledge transfer on cluster-level
```{r}
data_kt_five <- data_kt %>% filter(YEAR >=2001 & YEAR <=2020) %>%
  mutate(ID = ifelse(YEAR >= 2001 & YEAR <= 2005, 1, 
                                    ifelse(YEAR >= 2006 & YEAR <= 2010, 2, 
                                    ifelse(YEAR >= 2011 & YEAR <= 2015, 3, 
                                    ifelse(YEAR >= 2016 & YEAR <= 2020, 4,0)))))

data_kt_five %<>% select(COUNTRY, ID, n_kt) %>% group_by(COUNTRY, ID) %>% 
  summarise(across(.cols = everything(), ~ mean(.x, na.rm =TRUE)))

data_all %<>% left_join(data_kt_five, by = c("COUNTRY" = "COUNTRY", "ID" = "ID"))
```

correlation between dimensions and cocreation
```{r}
data_all %>% select(n_cocreate, INDICATOR_LIST, dim1, dim2, dim3) %>% ggcorr()
```


```{r}
data_all[,2:16] %>% select(n_kt, n_cocreate, INDICATOR_LIST, dim1, dim2, dim3) %>% ggpairs()
```

```{r}
data_all %>% group_by(cluster) %>% summarise(n = n(), avg = sum(n_kt, na.rm = TRUE) / n)
```


## Summary within cluster

```{r}
data_2 <- data_all %>% filter(cluster == 2)
```

```{r}
data_2[,c(1, 3:10, 12:13)] %>% group_by(COUNTRY) %>% 
  summarise(across(.cols = everything(), ~ mean(.x, na.rm = TRUE))) %>% 
  ggplot(aes(x = reorder(COUNTRY, n_kt.x), y = n_kt.x)) + 
  geom_col()
```



## STIP TRIANGULATION


```{r}
data_co %>% select(-COUNTRY, -YEAR) %>% na.omit() %>% ggpairs()
```

```{r}
data_co %>% select(n_cocreate, n_cocreate_lag1, n_cocreate_lag2, n_cocreate_lag3, INDICATOR_LIST, -COUNTRY, -YEAR) %>% na.omit() %>% ggcorr()
```

## Knowledge transfer

```{r}
data_kt %>% select(-COUNTRY, -YEAR) %>% ggpairs()
```


```{r}
data_kt %>% select( n_kt, n_kt_lag1, n_kt_lag2, n_kt_lag3, -COUNTRY, -YEAR, INDICATOR_LIST) %>% ggcorr()
```


## INDEX based on correlation

Creating index
```{r, include = FALSE}
data_co <- data_co %>% mutate(co_create = (GV_XFB + G_XGDP + GV_XGDP) / 3)
```



Plotting co-creation / knowledge transfer over time
```{r, include = FALSE}
co_create_df <- data_co %>% 
  filter(YEAR > 2000) %>% 
  group_by(YEAR) %>% 
  summarise(n = n(), co_avg = sum(co_create, na.rm =TRUE) / n) 


 co_create <- co_create_df %>%
  ggplot(aes(x = YEAR, y = co_avg)) + 
  geom_smooth(method = "loess") + 
  labs(y = "")
  theme_bw()

```

```{r}
co_create + 
  labs(y = "CC and KT Index")
```

```{r, include = FALSE}
co_create_country <- data_co %>% group_by(COUNTRY, YEAR) %>% 
  summarise(n = n(), co_avg = sum(co_create) / n) %>% ungroup() %>% 
  filter(co_avg > 1)


 
```

```{r}
co_create_country %>%  
  filter(YEAR == 2020) %>% 
  ggplot(aes(x = reorder(COUNTRY, co_avg), y = co_avg, fill = COUNTRY)) + 
  geom_col() + 
  labs(y = "CC and KT Index", x = "Country", title = "CC and KK in 2020 by country") +
  theme(legend.position = "none")
```

```{r}
data_co %>% ggplot(aes(x = YEAR, y = co_create)) + 
  geom_smooth(method = "loess", se = FALSE) + 
  theme(legend.position = "none")
```
